### 2018-04-14 dissertation/5-simulations/chapter5.tex
dissertation local revision

Eight desired properties for VANET trust models were presented in \autoref{section:properties}.
Here, TruMan's ability to satisfy each property is evaluated, ending with a final comparison between TruMan and previously proposed trust models for VANETs.

@@

\textit{3. Event/task and location/time dynamics}:
Aside from the time-related information used for information aging, dynamics were not used in the simulations presented here.
However, TruMan can be extended to consider event, task, location and time dynamics when managing trust.

@@

\textit{5. Integrated confidence measure}:
Since nodes using TruMan store trust values as a number between 0 and 1 that increase or decrease the more nodes interact (i.e. the more evidence they gather), this value can be used as a confidence measure of the opinion.
Setting the threshold $h$ to a value closer to 1 makes it unlikely that untrustworthy nodes will be incorrectly labeled as correct.

\textit{6. System level security}:
A public-private key solution can be used to verify message integrity.
This has not been considered in evaluations of TruMan.
However, it can be included as a separate security model during the transmission of messages.

@@

\textit{8. Robustness}: the model's resistance to attacks.
TruMan satisfies this property. Malicious nodes are quickly and accurately identified, making it difficult for them to perform attacks.
Experiments show that, when fewer than 50\% of nodes in the network are malicious, TruMan performs as expected.
Collusion attacks must be performed by more than half of the entire network, in which case the network is considered compromised.
Furthermore, since nodes take into consideration experiences from several trustworthy nodes, a malicious node that occasionally behaves correctly can still be identified.
Experiments with information aging show that it is possible to detect nodes that suddenly become malicious, although further experimentation with known attacks is still necessary.
%Furthermore, the analysis also takes into account the complexity of the algorithm necessary to implement the trust model, because a high priority of TruMan is the

@@

>>>>

Eight desired properties for VANET trust models were presented in \autoref{section:properties}.
Here, TruMan's ability to satisfy each property is evaluated.
\autoref{table:properties_truman} replicates the one from \autoref{section:properties} with the addition of TruMan, providing a full comparison between itself and the related work.

@@

\textit{3. Event/task and location/time dynamics}:
TruMan can be extended to consider event, task, location and time dynamics when managing trust.
However, aside from the time-related information used for information aging, dynamics were not used in the simulations presented here.

@@

\textit{5. Integrated confidence measure}:
Since nodes using TruMan store trust values as a number between 0 and 1 that increase or decrease the more nodes interact (i.e. the more evidence they gather), this value can be used as a confidence measure of the opinion.
Setting the threshold $h$ to a value closer to 1 makes it unlikely that malicious nodes will be incorrectly labeled as benign.

\textit{6. System level security}:
A public-private key solution can be used to verify message integrity, although it is not a requirement for the functioning of TruMan.
Any cryptographic solution can be integrated as a separate security model during the transmission of messages without affecting TruMan's efficiency and efficacy.

@@

\textit{8. Robustness}:
TruMan satisfies this property, because malicious nodes are quickly and accurately identified, making it difficult for them to perform attacks.
Experiments show that, when fewer than 50\% of nodes in the network are malicious, TruMan performs as expected.
Collusion attacks must be performed by more than half of the entire network, in which case the network is considered compromised.
Furthermore, since nodes take into consideration experiences from several trustworthy nodes, a malicious node that occasionally behaves correctly can still be identified.
Experiments with information aging show that it is possible to detect nodes that suddenly become malicious, although further experimentation with known attacks is still necessary.
%Furthermore, the analysis also takes into account the complexity of the algorithm necessary to implement the trust model, because a high priority of TruMan is the

@@

\begin{table}[t!]
\caption{Properties of the related work}
\label{table:properties_truman}
\centering
\begin{tabular}{|p{4cm}||p{0.5cm}|p{0.5cm}|p{0.5cm}|p{0.5cm}|p{0.5cm}|p{0.5cm}|p{0.5cm}|p{0.5cm}|}
 \hline
 \textbf{Property} & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8\\
 \hline
 \hline
 TruMan & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & - & - & \checkmark \\
 \hline
 \citep{dotzer2005vars} & \checkmark & - & \checkmark & - & - & - & \checkmark & -\\
 \hline
 \citep{minhas2010towards} & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & -\\
 \hline
 \citep{chen2010trust} & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & - & -\\
 \hline
 \citep{park2011long} & - & - & - & - & - & \checkmark & \checkmark & \checkmark \\
 \hline
 \citep{huang2014social} & \checkmark & - & \checkmark & \checkmark & \checkmark & - & - & -\\
 \hline
 \citep{li2016art} & \checkmark & - & - & - & \checkmark & - & - & \checkmark\\
 \hline
 \citep{chen2017cloud} & - & \checkmark & - & \checkmark & - & \checkmark & \checkmark & -\\
 \hline
\end{tabular}
\end{table}
